PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-08-03 main.tex
Small grammar edit.

To investigate whether any of these planetesimal disks underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each case. The ratio $m_{max}/\left< m \right>$ is plotted
in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
indicates that the growth rate is accelerating with mass, which is
evident at various times in all four cases. Even with a large value of
$\beta$, which means that the effective collision cross section is
very near the geometric value, runaway growth still appears to
operate. This seems to imply that, as bodies collide and grow, the
relative increase in their gravitational focusing factors, rather than
its absolute size, is what drives the system towards runaway
growth. Although larger encounter velocities will lengthen the growth
timescales, this mode of growth appears to be inevitable, so long as
gravity is the dominant force in the system.
% TRQ: also mention the negative slope

>>>>

To investigate whether any of these planetesimal disks underwent
runaway growth, we examine the time evolution of the maximum and mean
masses in each case. The ratio $m_{max}/\left< m \right>$ is plotted
in figure \ref{fig:alpha_beta_evo}. On this plot, a positive slope
indicates that the growth rate is accelerating with mass, which is
evident at various times in all four cases. Even with a large value of
$\beta$, which means that the effective collision cross section is
very near the geometric value, runaway growth still appears to
operate. This seems to imply that, as bodies collide and grow, the
relative increase in their gravitational focusing factors, rather than
their absolute size, is what drives the system towards runaway
growth. Although larger encounter velocities will lengthen the growth
timescales, this mode of growth appears to be inevitable, so long as
gravity is the dominant force in the system.
% TRQ: also mention the negative slope
